---
title: "Homework 4"
author: "Matt Corsetti"
date: "November 7, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

I first began tracking my weight on June 26th, 2016 to see how it might fluctuate as I began the first semester of my Ph.D. program at the University of Rochester in Rochester, NY. On June 26th I weigth 176 lbs. As of November 7th, I weighed 159.5 lbs.



### Data Collection

I collected the data by simply weighing myself as soon as I woke up. Measurements were unfortunately not taken every day. Also, the time of the measurement was not consistent. Some measurements were taken as early as 6:00AM while others were taken as late as 11:15AM. No food or liquids were consumed before weighing myself.

Each measurement was entered into the MyFitnessPal app which is provided for free by Under Armour. More information is provided here: <http://www.myfitnesspal.com/apps>.



## Data Analysis in R

### Reading in the Data
```{r}

### Libraries

   library(readxl)	# Hadley Wickham's package for reading in excel files
   library(ggplot2)	# ggplot2 - nice plots
   library(xtable)  # makes for nice tables


### Directories

   dir.data <- 'C:/Users/Matt/Desktop/My Documents/U of R/BST 494 - Statistical Computing/Data/'


### Read in Weight Data

   w <- read_excel(c(paste0(dir.data, 'Matt Corsetti - Weight Data.xlsx')))
   str(w)
   
```
   
   
### Summary Statistics
```{r}

   summary(w$Weight)

```

```{r, echo = FALSE}

   ggplot(w, aes(x = Weight)) +
     geom_histogram(fill = 'dark blue', col = 'light grey', binwidth = 1) +
     xlab('\nWeight\n') +
     ylab('Count\n') +
     ggtitle("\nDistribution of Matt's Weight Measurements\n") +
     theme(panel.background = element_rect(fill = 'dark grey'),
           panel.grid.major = element_line(color = 'grey'),
           panel.grid.minor = element_blank(),
           plot.background = element_rect(fill = 'black'),
           plot.title = element_text(color = 'light grey', size = 15),
           axis.title.y = element_text(color = 'light grey', angle = 0),
           axis.title.x = element_text(color = 'light grey'),
           legend.background = element_rect(fill = 'black'),
           legend.text = element_text(color = 'light grey'),
           legend.title = element_text(color = 'light grey'),
           axis.text.x = element_text(color = 'light grey'),
           axis.text.y = element_text(color = 'light grey'))

```

### Weight Measurement Data

```{r, echo = FALSE}

  ggplot(w, aes(x = Date, y = Weight)) +
    geom_line(col = 'red') +
    geom_point() +
    xlab('\nDate of Measurement\n') +
    ylab('Weight\n') +
    ggtitle("\nMatt's Weight From Summer to Winter\n(Linear Regression)\n") +
    theme(panel.background = element_rect(fill = 'dark grey'),
      panel.grid.major = element_line(color = 'grey'),
		  panel.grid.minor = element_blank(),
		  plot.background = element_rect(fill = 'black'),
		  plot.title = element_text(color = 'light grey', size = 15),
		  axis.title.y = element_text(color = 'light grey', angle = 0),
		  axis.title.x = element_text(color = 'light grey'),
		  legend.background = element_rect(fill = 'black'),
		  legend.text = element_text(color = 'light grey'),
		  legend.title = element_text(color = 'light grey'),
		  axis.text.x = element_text(color = 'light grey'),
		  axis.text.y = element_text(color = 'light grey'))
		  
```




### Linear Regression Model

Having plotted the data, a linear regression model appears to be a decent model candidate. The steps below show the creation and summary of a linear regression model for the weight data. A plot which overlays the regression model atop the observed data points is also provided.

```{r, results = 'asis'}

  lm.w <- lm(Weight ~ Date, data = w)
  cat('Adjusted R-sq:', summary(lm.w)$adj.r.squared)
  print(xtable(summary(lm.w)), type = 'html')
   
```

```{r, echo = FALSE}

  ggplot(w, aes(x = Date, y = Weight)) +
    geom_smooth(method = 'lm', formula = y ~ x, data = w, se = FALSE) +
    geom_line(col = 'red') +
    geom_point() +
    xlab('\nDate of Measurement\n') +
    ylab('Weight\n') +
    ggtitle("\nMatt's Weight From Summer to Winter\n(Linear Regression)\n") +
    theme(panel.background = element_rect(fill = 'dark grey'),
      panel.grid.major = element_line(color = 'grey'),
		  panel.grid.minor = element_blank(),
		  plot.background = element_rect(fill = 'black'),
		  plot.title = element_text(color = 'light grey', size = 15),
		  axis.title.y = element_text(color = 'light grey', angle = 0),
		  axis.title.x = element_text(color = 'light grey'),
		  legend.background = element_rect(fill = 'black'),
		  legend.text = element_text(color = 'light grey'),
		  legend.title = element_text(color = 'light grey'),
		  axis.text.x = element_text(color = 'light grey'),
		  axis.text.y = element_text(color = 'light grey'))

```


### Loess Curve

Here we provide the Loess Curve to the weight data and plot it atop the observed data points.

```{r, echo = FALSE}

  ggplot(w, aes(x = Date, y = Weight)) +
	  geom_smooth(method = 'loess', formula = y ~ x, data = w, se = FALSE) +	
    geom_line(col = 'red') +
    geom_point() +
	  xlab('\nDate of Measurement\n') +
	  ylab('Weight\n') +
	  ggtitle("\nMatt's Weight From Summer to Winter\n(Loess Curve)\n") +
	  theme(panel.background = element_rect(fill = 'dark grey'),
		  panel.grid.major = element_line(color = 'grey'),
		  panel.grid.minor = element_blank(),
		  plot.background = element_rect(fill = 'black'),
		  plot.title = element_text(color = 'light grey', size = 15),
		  axis.title.y = element_text(color = 'light grey', angle = 0),
		  axis.title.x = element_text(color = 'light grey'),
		  legend.background = element_rect(fill = 'black'),
		  legend.text = element_text(color = 'light grey'),
		  legend.title = element_text(color = 'light grey'),
		  axis.text.x = element_text(color = 'light grey'),
		  axis.text.y = element_text(color = 'light grey'))

```

